\documentclass[landscape]{article}
\usepackage{ve482}

\title{VE482 --- Introduction to\\ Operating Systems}
\subtitle{Payroll (Team {{ team }})}
\semester{Fall}
\year{2020}
\blockinfo{
	\begin{center}
		\textbf{Salary conditions}
	\end{center}
	\begin{itemize}\itemsep .25cm
		\item Documentation (30 pts)
		\item Correctness (30 pts)
		\item Performance (90 pts)
		\item Contribution
	\end{itemize}
}

% whether or not to display the instructor line
\noinstructor

\begin{document}
\maketitle

\section{Documentation}

Not included in this report.

\section{Correctness}

In the listen queries, {\color{red}TLE} means that your program is not able to respond to queries piped into the listened files.

\begin{table}[!htbp]
\centering
{{ correctness }}
\caption{Result of correctness cases.}
\end{table}

\newpage

\section{Performance}

In the performance test, any error will lead to zero for the test case. The fastest and slowest time for each case are omitted.

{\color{red}TLE} means that your program exceeds 1.2 times of the single thread base program so it is unnecessary to test this case anymore.

\begin{table}[!htbp]
\centering
{{ performance }}
\caption{Result of performance cases.}
\end{table}

\section{Contribution}

The git commits analysis only considered C/C++ source files. It will not consider the commits whose authors are not included in the commit.json of the project. 
The total contribution percentage may not be 100\% since there is an initial commit from the git server admin.
Other contributions (eg. documentation) can also be considered besides.

\begin{table}[!htbp]
\centering
{{ contribution }}
\caption{Result of git commits analysis.}
\end{table}

\newpage

\section*{Appendix}

Tested on {{ platform }}, with {{ cpu }}, {{ threads }} threads and {{ memory }} memory.

All files are stored on a memory-based fs.

The source code of the test framework can be found on \url{https://github.com/tc-imba/VE482-p2-testcase}. \bigskip

Error Names:
\begin{itemize}
\item {\color{red}CE}: Compile Error
\item {\color{red}TLE}: Time Limit Exceeded
\item {\color{red}RTE}: Runtime Error
\item {\color{red}WA}: Wrong Answer
\end{itemize}

\section*{Git Log}

\begin{multicols}{2}
{{ log }}
\end{multicols}

\end{document}
